---
title: "Simple Example"
author: "Ethan Violette"
date: "12/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = TRUE,
                      message = FALSE)
source("../RNHANES_Helper.R")
#install.packages("ggplot2")
library(ggplot2)
```

Let's say I wanted to look at if a relationship exists between Nicotine Consumption and Estradiol, an estrogen steroid hormone. 
I'll begin by searching through the variables for both:

```{r find-vars}
nhanes_search(variables, "Estradiol")
unique(nhanes_search(variables, "Nicotine")$variable_description)
```

I find that the variable name for participant serum estradiol concentration is SSSE2; the variable name for the participant consuming nicotine in the past five days is SMQ680.

Now I can use the nhanes.merg.data() function to find all datasets that contain these two variables, and merge them by participant ID so I can examine the relationship. The arguments to the function are as follows:

- Variable List: c("SMQ680", "SSSE2")
- Periods: "all"
- Variable Naming: c("Days.Nicotine", "Estradiol")
- Remove NA values: TRUE
- Remove outliers for certain variables: c(FALSE, TRUE)

```{r}
df.test <- nhanes.merg.data(c("SMQ680", "SSSE2"), 
                      "all",  
                      c("Days.Nicotine", "Estradiol"),
                      TRUE,
                      c(FALSE, TRUE))

summary(df.test)
```

From here any sort of analysis can be done.

```{r}
df.test <- df.test[df.test$Estradiol > 0 & df.test$Days.Nicotine <= 5,]

df.test$Days.Nicotine <- as.factor(df.test$Days.Nicotine)

levels(df.test$Days.Nicotine) <- c("Yes", "No")

ggplot(df.test, aes(x = Days.Nicotine, y = Estradiol)) + geom_boxplot()
```

